%-------------------------
% Resume in Latex
% Author : Souradeep Banerjee
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%----------FONT OPTIONS----------
% (Uncomment only one to change font style)
% \usepackage[sfdefault]{FiraSans}  % sans-serif
% \usepackage{CormorantGaramond}    % serif

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% --- OPTIMIZATION 1: MAXIMIZE PAGE USAGE ---
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- OPTIMIZATION 2: SECTION SPACING ---
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% --- OPTIMIZATION 3: LIST SPACING ---
% This pulls bullet points closer together
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=-1pt, leftmargin=0.15in]} % Tighter items
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Souradeep Banerjee} \\ \vspace{2pt}
    \small (480) 743-3328 $|$ \href{mailto:sbaner92@asu.edu}{\underline{sbaner92@asu.edu}} $|$
    \href{https://souradeep.dev/}{\underline{souradeep.dev}} $|$
    \href{https://linkedin.com/in/souradeep1101}{\underline{linkedin.com/in/souradeep1101}} $|$
    \href{https://github.com/souradeep1101}{\underline{github.com/souradeep1101}} \\ \vspace{4pt}
    \small \textbf{F-1 Visa $|$ Eligible for CPT \& 36-month STEM OPT}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, Arizona}
      {Bachelor of Science, Computer Science (Concentration: Software Engineering)}{Expected May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{GPA: 3.53}; Dean's List; New American University Scholar}
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Computer Architecture, Operating Systems, Competitive Programming.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{Jan 2023 -- Jan 2024}
      {Cruv.org}{Kolkata, India (Remote)}
      \resumeItemListStart
      \resumeItem{Delivered \textbf{2} full-scale client-side applications, reducing UI state bugs by an estimated \textbf{30\%}, by establishing robust state management architectures using Flutter and Dart.}
      \resumeItem{Achieved a consistent \textbf{60 FPS} rendering baseline on constrained mobile devices, decreasing frame drop rates by \textbf{40\%}, by aggressively profiling and optimizing custom animation loops within the Flutter framework.}
      \resumeItem{Accelerated feature development timelines by roughly \textbf{20\%} by evaluating, debugging, and seamlessly integrating \textbf{5} complex third-party open-source Flutter libraries into proprietary codebases.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    
    \resumeProjectHeading
      {\textbf{Cyclops MIPS (Cycle-Accurate CPU Emulator)} $|$ \emph{C++23, ImGui, GTest, CMake}}{Nov 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Architected a strictly-typed \textbf{MIPS R2000 simulator} capable of executing binary machine code with full support for \textbf{5-Stage Pipelining}, Data Hazards, and Branch Delay Slots.}
        \resumeItem{Implemented a \textbf{Forwarding Unit} and \textbf{Hazard Detection Unit} to resolve data dependencies without stalling, optimizing Instructions Per Cycle (IPC) throughput.}
        \resumeItem{Designed a \textbf{Virtual Memory Management Unit (MMU)} with a Translation Lookaside Buffer (TLB) to simulate paging and memory protection faults.}
        \resumeItem{Implemented a custom \textbf{Two-Pass Assembler} in C++ to parse MIPS source code, resolve symbol labels, and generate binary machine code, enabling direct execution of user programs.}
        \resumeItem{Validated hardware correctness via \textbf{Google Test (GTest)} against edge cases (overflow, unaligned access) and developed a real-time \textbf{ImGui Dashboard} for cycle-by-cycle pipeline debugging.}
      \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Cyclops Studio (High-Performance Animation Engine)} $|$ \emph{C++23, OpenGL 4.6, ImGui, CMake}}{Oct 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Architected a \textbf{Data-Oriented rendering pipeline} using Modern OpenGL 4.6 (DSA), utilizing \textbf{Batch Rendering} and dynamic vertex streaming to saturate GPU bus bandwidth, achieving seamless \textbf{4K/144 FPS}.}
        \resumeItem{Engineered a zero-copy \textbf{Layer Compositing System} using custom Framebuffer Objects (FBOs) and separate blend states, decoupling the high-frequency simulation loop from the display rasterization stage.}
        \resumeItem{Designed a cache-coherent \textbf{Particle Simulation Engine} capable of handling \textbf{100k+ concurrent entities} by implementing a custom \textbf{Linear Arena Allocator}, eliminating heap fragmentation and cache misses.}
        \resumeItem{Built a robust \textbf{Asset Serialization System} (YAML) with hot-reloading capabilities for brush dynamics, integrated into a modular \textbf{ImGui Docking} workspace to accelerate technical artist workflows.}
    \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Joint DiT (Multimodal Diffusion Model)} $|$ \emph{Python, PyTorch, CUDA}}{Jul 2025 -- Oct 2025}
      \resumeItemListStart
          \resumeItem{Engineered a multimodal diffusion architecture, expanding maximum sequence length by \textbf{300\%} without Out-Of-Memory (OOM) crashes, by implementing aggressive \textbf{KV-cache optimization} and query chunking on single-GPU setups.}
          \resumeItem{Optimized cross-modal feature synchronization, reducing matrix computation overhead by \textbf{40\%}, by designing and implementing custom, memory-efficient \textbf{attention masks}.}
          \resumeItem{Accelerated iteration cycles by automating deployment and documentation, saving an estimated \textbf{5 hours per week} in developer overhead, by establishing a robust \textbf{CI/CD pipeline} and Gradio interface.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP & ACHIEVEMENTS-----------
\section{Leadership \& Achievements}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {ICPC Rocky Mountain Regional Contest 2025}{Nov 2025 -- Nov 2025}
      {Selected to represent ASU as a regional finalist; competed against top university teams in the region.}{Tempe, AZ}

    \resumeSubheading
      {Manager of Industry Programs, ACM at ASU}{Oct 2025 -- Present}
      {Lead technical operations and industry relations; automated internal newsletters using \textbf{Docker/React}.}{Tempe, AZ}

    \resumeSubheading
      {ICPC North American Qualifier (NAQ) 2025, 2nd Place Finisher}{Oct 2025 -- Oct 2025}
      {Secured 2nd Place (ASU Site) by solving 5 algorithmic problems under strict time constraints.}{Tempe, AZ}

    \resumeSubheading
      {CodePath Advanced Software Engineering (TIP 102)}{Aug 2025 -- Dec 2025}
      {Earned ``Advanced'' certification (Top 5\%) for mastering complex graph algorithms and DP.}{Tempe, AZ}
      
    \resumeSubheading
      {Grand Challenges Scholars Program (AI Scholar)}{Aug 2024 -- Present}
      {Conducting interdisciplinary research on Generative AI applications for the ``Joy of Living'' theme.}{Tempe, AZ}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++ (17/20/23), C, Assembly (MIPS), Python, SQL, Java, Dart, JavaScript/TypeScript} \\
     \textbf{Systems \& Cloud}{: Linux (Kernel/User), Docker, Kubernetes, AWS, CMake, GDB, CI/CD, Git} \\
     \textbf{Libraries \& Frameworks}{: OpenGL, ImGui, STL, PyTorch, React.js, Node.js, Flutter, Next.js} \\
     \textbf{Concepts}{: Computer Architecture, OS Internals, Concurrency, Memory Management, Distributed Systems}
    }}
 \end{itemize}

\end{document}